---
title: "Online MLQ analysis"
author: "Joshua Clingo"
date: "5/27/2021"
output:
  html_document: default
  pdf_document: default
bibliography: bibliography.json
---

```{r include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=TRUE)
```

```{r setup, include=FALSE}
library(tidyverse)
# library(lme4)
library(lsr)
library(corrplot)
library(ggeffects)
options(mc.cores = parallel::detectCores())
theme_set(theme_classic()) 
set.seed(123)

```





```{r echo=FALSE}

# read in data

filename = file.choose()
df = readRDS(filename)

df_mlq = df %>% 
  filter(!is.na(MLQ_1)) %>% 
  select (., -(AWE_1:AWE_DO), -AWE, -AWE_Time, -AWE_SelfLoss, -AWE_Connectedness) 

df_awe = df %>% 
  filter(!is.na(AWE_1)) %>% 
  select (., -(MLQ_1:MLQ_DO), -MLQ, -MLQ_Presence, -MLQ_Search)

```

```{r}

regressor = lm(formula = MLQ ~ Condition + IsFemale + Age + ReligiousScale + HasTakenPsychedelic, data = df_mlq)
summary(regressor)

```

```{r}

regressor = lm(formula = AWE ~ Condition + IsFemale + Age + ReligiousScale + HasTakenPsychedelic, data = df_awe)
summary(regressor)

```


```{r}

boxplot(MLQ~Condition,data=df_mlq, main="MLQ Per Condition",
   xlab="Condition", ylab="MLQ")

boxplot(MLQ_Presence~Condition,data=df_mlq, main="MLQ Presence Per Condition",
   xlab="Condition", ylab="MLQ")

boxplot(MLQ_Search~Condition,data=df_mlq, main="MLQ Search Per Condition",
   xlab="Condition", ylab="MLQ")

```

```{r}

df_mlq_not_bad = df_mlq %>%
  filter(ParticipantID != 145317216, 
         ParticipantID != 150787919,
         ParticipantID != 104528162,
         ParticipantID != 121475818,
         ParticipantID != 119803467,
         ParticipantID != 150693715,
         ParticipantID != 136011243,
         ParticipantID != 151831974,
         ParticipantID != 192762097
         )

boxplot(MLQ~Condition,data=df_mlq_not_bad, main="MLQ Per Condition",
   xlab="Condition", ylab="MLQ")

boxplot(MLQ_Presence~Condition,data=df_mlq_not_bad, main="MLQ Presence Per Condition",
   xlab="Condition", ylab="MLQ")

boxplot(MLQ_Search~Condition,data=df_mlq_not_bad, main="MLQ Search Per Condition",
   xlab="Condition", ylab="MLQ")

```

```{r echo=FALSE}

df_mlq_main = df_mlq %>%
  filter(Condition == 0)

df_mlq_control = df_mlq %>%
  filter(Condition == 1)

df_mlq_baseline = df_mlq %>%
  filter(Condition == 2)


```


```{r echo=FALSE}

df_awe_main = df_awe %>%
  filter(Condition == 0)

df_awe_control = df_awe %>%
  filter(Condition == 1)

boxplot(AWE~Condition,data=df_awe, main="AWE-S Per Condition",
   xlab="Condition", ylab="AWE-S")

boxplot(AWE_Time~Condition,data=df_awe, main="AWE-S Per Condition",
   xlab="Condition", ylab="AWE-S")

boxplot(AWE_SelfLoss~Condition,data=df_awe, main="AWE-S Per Condition",
   xlab="Condition", ylab="AWE-S")

boxplot(AWE_Connectedness~Condition,data=df_awe, main="AWE-S Per Condition",
   xlab="Condition", ylab="AWE-S")



```



```{r echo=FALSE}

df_awe_not_bad = df_awe %>%
  filter(ParticipantID != 145317216, 
         ParticipantID != 150787919,
         ParticipantID != 104528162,
         ParticipantID != 121475818,
         ParticipantID != 119803467,
         ParticipantID != 150693715,
         ParticipantID != 136011243,
         ParticipantID != 151831974,
         ParticipantID != 192762097
         )

df_awe_main = df_awe_not_bad %>%
  filter(Condition == 0)

df_awe_control = df_awe_not_bad %>%
  filter(Condition == 1)

boxplot(AWE~Condition,data=df_awe_not_bad, main="AWE-S",
   xlab="Condition", ylab="AWE-S")

boxplot(AWE_Time~Condition,data=df_awe_not_bad, main="AWE-S - Time",
   xlab="Condition", ylab="AWE-S")

boxplot(AWE_SelfLoss~Condition,data=df_awe_not_bad, main="AWE-S - Loss of Self",
   xlab="Condition", ylab="AWE-S")

boxplot(AWE_Connectedness~Condition,data=df_awe_not_bad, main="AWE-S - Connectedness",
   xlab="Condition", ylab="AWE-S")



```



```{r echo=FALSE}

# I understand my life's meaning
mean(df_mlq_main$MLQ_1)
mean(df_mlq_control$MLQ_1)
mean(df_mlq_baseline$MLQ_1)

# I am looking for something that makes my life feel meaningful
mean(df_mlq_main$MLQ_2)
mean(df_mlq_control$MLQ_2)
mean(df_mlq_baseline$MLQ_2)

# I am always looking to find my life's purpose
mean(df_mlq_main$MLQ_3)
mean(df_mlq_control$MLQ_3)
mean(df_mlq_baseline$MLQ_3)

# My life has a clear sense of purpose
mean(df_mlq_main$MLQ_4)
mean(df_mlq_control$MLQ_4)
mean(df_mlq_baseline$MLQ_4)

# I have a good sense of what makes my life meaningful
mean(df_mlq_main$MLQ_5)
mean(df_mlq_control$MLQ_5)
mean(df_mlq_baseline$MLQ_5)



```



```{r}

df %>% 
  mutate(IsBeliever = if_else(ReligiousScale >= 50, 1, 0)) %>% 
  ggplot() + 
  geom_bar(aes(x=IsCorrect, fill=factor(IsBeliever))) + 
  ggtitle(label = "MEQ Score vs Religiosity across both conditions",
          subtitle = "(Inc. whether they got the answer right or not)") +
  facet_wrap(~IsBelieverCondition, labeller = as_labeller(c("0" = "Non-believer Condition", "1" = "Believer Condition" )))


```

```{r}
glm =  glm(IsCorrect ~ IsBelieverCondition, data=df, family = binomial(link = "logit"))
summary(glm)
```

```{r}
# Simple Generalized Linear Mixed-Effects Model
gmm <- glmer(data = df, 
              family = binomial(link = "logit"), 
              IsCorrect ~ 1 + 
              IsBelieverCondition + 
              (IsBelieverCondition|ReligiousScale))
```

```{r echo=FALSE}
summary(gmm)
```

```{r}
# Simple Generalized Linear Mixed-Effects Model
gmm <- glmer(data = df, 
              family = binomial(link = "logit"), 
              IsCorrect ~ 1 + 
              IsBelieverCondition + 
              (IsBelieverCondition|ReligiousScale))
```

```{r echo=FALSE}
summary(gmm)
```

```{r}
cor(df$ReligiousScale, df$MEQ_Score)
```

```{r echo=FALSE}

levels(df$IsCorrect) <- list("False" = "0",        # Change factor levels
                               "True" = "1")

p2 = df %>% 
  ggplot(aes(x=ReligiousScale, y=MEQ_Score)) + 
  geom_point(aes(color=factor(IsCorrect)), alpha=0.8) + 
  ggtitle(label = "MEQ Score vs Religiosity across both conditions", 
          subtitle = "Each point represents a single participant") +
  labs(x = "Self-reported belief in God/gods (0-100)", 
       y = "MEQ Score") +
  scale_colour_manual(name = "Got the right answer", values = c("#f44336", "#4CAF50")) +
  geom_line(stat="smooth",method = "lm", formula = y~x,
              size = 1,
              alpha = 0.2) +
  facet_wrap(~IsBelieverCondition, labeller = as_labeller(c("0" = "Group A", "1" = "'Group B" )))

```


```{r}
ggsave(p2, file="MEQ vs Religiosity.png", width=8, height=4)
```

```{r echo=FALSE, out.width="50%"}
df_correlations = df %>% 
  select(IsCorrect, IsBelieverCondition, MEQ_Score, ReligiousScale, `Duration (in seconds)`, IsFemale, Education, Psychedelic)
df_correlations[] <- lapply(df_correlations,as.integer)
res1 <- cor.mtest(df_correlations, conf.level = .95)
## specialized the insignificant value according to the significant level
corrplot(cor(df_correlations), p.mat = res1$p, insig = "label_sig",
         sig.level = c(.001, .01, .05), pch.cex = .9, pch.col = "white")
```

```{r echo=FALSE ,out.width="50%"}
df_correlations = df_believer %>% 
  select(IsCorrect, MEQ_Score, ReligiousScale, `Duration (in seconds)`, IsFemale, Education, Psychedelic)
df_correlations[] <- lapply(df_correlations,as.integer)
res1 <- cor.mtest(df_correlations, conf.level = .95)
## specialized the insignificant value according to the significant level
corrplot(cor(df_correlations), p.mat = res1$p, insig = "label_sig",
         sig.level = c(.001, .01, .05), pch.cex = .9, pch.col = "white")
```


```{r echo=FALSE, out.width="50%"}
df_correlations = df_nonbeliever %>% 
  select(IsCorrect, MEQ_Score, ReligiousScale, `Duration (in seconds)`, IsFemale, Education, Psychedelic)
df_correlations[] <- lapply(df_correlations,as.integer)
res1 <- cor.mtest(df_correlations, conf.level = .95)
## specialized the insignificant value according to the significant level
corrplot(cor(df_correlations), p.mat = res1$p, insig = "label_sig",
         sig.level = c(.001, .01, .05), pch.cex = .9, pch.col = "white")
```

```{r echo=FALSE, out.width="50%"}
df %>% 
  ggplot()+
  ggtitle(label = "Accuracy by condition")+
  stat_summary(aes(x = IsCorrect, y = ReligiousScale, group = IsBelieverCondition), geom = "point", alpha = 0.5)+
  stat_summary(aes(x = IsCorrect, y = ReligiousScale, group = IsBelieverCondition), geom = "line", alpha = 0.5)+
  stat_summary(aes(x = IsCorrect, y = ReligiousScale), geom = "pointrange", color = "red") +
  facet_wrap(~IsBelieverCondition, labeller = as_labeller(c("0" = "Group A", "1" = "Group B" ))) +
    labs(y = "Self-reported belief in God/gods (0-100)", 
       x = "",
       subtitle = "(correct if chose 'This woman is a teacher')")

```


## Modeling

### First we take the combined results and treat the condition as a random effect

```{r}
# Simple Generalized Linear Mixed-Effects Model
gmm <- glmer(data = df, 
              family = binomial(link = "logit"), 
              IsCorrect ~ 1 + 
              ReligiousScale +
              MEQ_Score +
              (1|Race) +
              (1|IsBelieverCondition) +
              (1|IsFemale) + 
              (1|Age))
```

```{r echo=FALSE}
summary(gmm)
```

Given our model, these are our predictions for the two main predictors of respondents getting the correct answer

```{r echo=FALSE, out.width="50%"}
pred_religious <- ggpredict(gmm, "ReligiousScale")
plot(pred_religious)
```

```{r echo=FALSE, out.width="50%"}
pred_meq <- ggpredict(gmm, "MEQ_Score")
plot(pred_meq)
```
As you can see, the confidence intervals are rather wide but the trend is quite clear and strong. 
More belief and/or mystical feeling leads to a higher predicted error rate. (We break this down by condition in the Appendix)

### Results discussion

## Hypotheses
* (check) We expected those in the believer condition to commit the conjunction error at 
a much higher rate than those in the non-believer condition, regardless of personal believe in God/gods
* ~ We expected believer people in the non-believer condition to commit the error slightly less than those who self-rated low belief in God/gods
* (check) We expected MEQ scores to correlate somewhat strongly with belief in God/gods


- Right, so our predictions were more or less correct!
- Only hangup here was our low power when it came to predicting religiosity under the non-belief condition

This is just the first of a series of follow-ups where we're going to be looking into
ways to better validate whether we're really getting at eudaemonia (instead of unintentionally retreading the prosocial work that's already well-established)

### Appendix (read if you want)

### Delving into differences

Here we pull the groups apart--we committed ourselves to this approach with the conjunction effect we've espoused. 
Here's for the believer data:

```{r echo=FALSE}

# Simple Generalized Linear Mixed-Effects Model
gmm_believer <- glmer(data = df_believer, 
              family = "binomial", 
              IsCorrect ~ 1 + 
              ReligiousScale +
              MEQ_Score +
              (1|IsFemale) +
              (1|Race) +
              (1|Age))

Anova(gmm_believer, type="3")

```

Now we'll plot the correctness probabilities for each condition.

### Believer Condition

```{r echo=FALSE, out.width="50%"}
pred_religious <- ggpredict(gmm_believer, "ReligiousScale")
plot(pred_religious)
```
```{r echo=FALSE, out.width="50%"}
pred_meq <- ggpredict(gmm_believer, "MEQ_Score")
plot(pred_meq)
```

### Nonbeliever Condition

```{r echo=FALSE}

# Simple Generalized Linear Mixed-Effects Model
gmm_nonbeliever <- glmer(data = df_nonbeliever, 
              family = "binomial", 
              IsCorrect ~ 1 + 
              ReligiousScale +
              MEQ_Score +
              (1|IsFemale) +
              (1|Race) +
              (1|Age))

Anova(gmm_nonbeliever, type="3")

```

```{r echo=FALSE, out.width="50%"}
pred_religious <- ggpredict(gmm_nonbeliever, "ReligiousScale")
plot(pred_religious)
```

```{r echo=FALSE, out.width="50%"}
pred_meq <- ggpredict(gmm_nonbeliever, "MEQ_Score")
plot(pred_meq)
```
We're given a strikingly different perspective once we pull these apart. What really seems to
matter is not their religiosity but their *religiosity when confronted with a bias-affirming option*. 

### Model check!

Combined condition model accuracy
```{r echo=FALSE}
# Make some predictions
df$predictions <- predict(gmm, type = "response")
df$predictions_IsCorrect = ifelse(df$predictions > 0.5, 1, 0)
df$accuracy = df$predictions_IsCorrect == df$IsCorrect

mean(df$accuracy)
```

Believer condition model accuracy
```{r}
# Make some predictions
df_believer$predictions <- predict(gmm_believer, type = "response")
df_believer$predictions_IsCorrect = ifelse(df_believer$predictions > 0.5, 1, 0)
df_believer$accuracy = df_believer$predictions_IsCorrect == df_believer$IsCorrect

mean(df_believer$accuracy)
```

Non-believer condition model accuracy
```{r}
# Make some predictions
df_nonbeliever$predictions <- predict(gmm_nonbeliever, type = "response")
df_nonbeliever$predictions_IsCorrect = ifelse(df_nonbeliever$predictions > 0.5, 1, 0)
df_nonbeliever$accuracy = df_nonbeliever$predictions_IsCorrect == df_nonbeliever$IsCorrect

mean(df_nonbeliever$accuracy)
```


Distribution of belief
```{r}

df %>% 
  mutate(MeanBelief = mean(ReligiousScale)) %>% 
  ggplot(aes(x=ReligiousScale, fill=IsCorrect, color=IsCorrect)) + 
  geom_histogram(binwidth=1) + 
  geom_vline(mapping =aes(xintercept = MeanBelief), linetype="dashed", 
                color = "black", size=1)
```

```{r}

p4 = df %>% 
  mutate (Correct = if_else(as.numeric(as.character(IsCorrect)) == 1, "True", "False")) %>% 
  mutate(MeanBelief = mean(ReligiousScale)) %>% 
  ggplot(aes(x=ReligiousScale, fill=IsCorrect)) + 
  geom_histogram(binwidth=1.5) + 
  facet_wrap(~IsBelieverCondition ,labeller = as_labeller(c("0" = "Group A", "1" = "Group B" ))) + 
  scale_fill_manual(values = c("False" = "#f44336",
                               "True" = "#4CAF50")) +
  geom_vline(mapping =aes(xintercept = MeanBelief), linetype="dashed", 
                color = "black", size=1) +
  labs(x='Self-reported belief in God/gods (0-100)',
       title='Relative accuracy', fill='Responded correctly')
```
```{r}
ggsave(p4, file="Religiosity vs Responses.png", width=8, height=4)
```


```{r}
mean(df$ReligiousScale)
```

